Think deep for reef resilience

### 2025-08-06 paper/paper_draft.qmd
Expand on GCM information and add basic table with ECS values.

The five selected GCMs span a range of Equilibrium Climate Sensitivity (ECS) values within
the IPCC assessed likely range, and GCM development families. The IPCC defines ECS as the
long term warming caused by a doubling of carbon dioxide above its pre-industrial
concentration [@forster2021]. The five GCMs therefore allow for a range of possible climate
futures to be explored, capturing the uncertainty in future responses to CO2 increases
(@sfig-ecs; @sfig-methods-dhws; [@grose2023; @shepherd2018]).

Shared Socio-economic Pathway 2 (replacing the older RCP 4.5) was used to represent the
plausible emission pathway under current emission trajectories, with similar atmospheric CO2
levels remaining until 2050 [@hausfather2020; IPCC -@climate2023]. \[**TI note: The above
needs to be expanded a little. IPCC has not been mentioned before at this point either**\]

@@

@@

<!-- Split and move below to results/discussion -->

>>>>

The five selected GCMs span a range of Equilibrium Climate Sensitivity (ECS) values within
the Intergovernmental Panel on Climate Change (IPCC) assessed likely range, and GCM
development families. The IPCC defines ECS as the long term warming caused by a doubling of
carbon dioxide above its pre-industrial concentration [@forster2021]. The five GCMs
therefore allow for a range of possible climate futures to be explored, capturing the
uncertainty in future responses to CO2 increases (@sfig-ecs; @sfig-methods-dhws;
[@grose2023; @shepherd2018]).

Shared Socio-economic Pathway 2-4.5 (approximate to the previously used RCP 4.5) was used to
represent the plausible emission pathway under current emission trajectories, with similar
atmospheric CO2 levels to present day remaining until 2050 [@hausfather2020; IPCC
-@climate2023]. This SSP trajectory estimates 2.7°C of global atmospheric warming in the
2081-2100 period relative to 1850-1900.

\[**TI note: The above needs to be expanded a little. IPCC has not been mentioned before at this point either**\]

@@

| Global Climate Model source | ECS value (°C) | Interpreted relative severity | Individual results displayed |
|----|----|----|----|
| EC-Earth3-Veg | 4.31 | High | Supplementary |
| ACCESS-ESM1-5 | 3.87 | Intermediate | Supplementary |
| ACCESS-CM2 | 4.72 | High | Main text |
| GFDL-CM4 | 2.9 | Low | Supplementary |
| NorESM2-MM | 2.5 | Low | Supplementary |

: Table 1: Information for each GCM used in this investigation including ECS value,
interpreted relative severity and where results are individual GCM results are displayed. GCMs in context with assessed plausible ranges of ECS values are displayed in [@fig-ecs].
ACCESS-ESM1-5 is taken as an intermediate model based on the range of ECS values, thus
results are displayed in the main text. ECS value sources: .

\[**BG: Need to add my ECS value sources to table caption. (And also cite GCM paper sources).**\]

@@
